%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\usepackage{array}
\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{38}{47}} 
\newcolumntype{L}{>{\hb@xt@\z@\bgroup}l<{\hss\egroup}}
\newcolumntype{C}{>{\centering\arraybackslash}c}
\newcolumntype{R}{>{\hb@xt@\z@\bgroup\hss}r<{\egroup}}
\makeatother

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{L@{\extracolsep{\fill}}C@{\extracolsep{\fill}}R}
  \href{mailto:mtejas619@gmail.com}{mtejas619@gmail.com} &
  \multirow{3}{*}{\Huge \textbf{Tejas Mankeshwar}} &
  \href{https://www.linkedin.com/in/tejasmankeshwar}{LinkedIn/tejasmankeshwar} \\
  (+91) 87673 83170 & & \href{https://github.com/TejasMankeshwar}{GitHub/TejasMankeshwar} \\
  Indian Citizen & & \href{https://tejasmankeshwar.github.io/Website-Portfolio/}{Portfolio} \\
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education }
  \resumeSubHeadingListStart
    \resumeSubheading
      {Savitribai Phule University}{Pune, MH}
      {B.E in Computer Science, GPA: 9.2/10}{Sept 2022 -- May 2026}
      \resumeItemListStart
        \resumeItem{Concentrations}{Artificial Intelligence \& Machine Learning }
        \resumeItem{Coursework}
          {Data Structures \& Algorithms, Object-Oriented Programming, Objects \& Software Design, Cloud Computing,  Systems \& Networks, Design \& Analysis of Algorithms, Database Systems, Statistics, Advance Mathematics, Big Data Analytics, High Performance Computing, Natural Language Processing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ProjectPro}{Bengaluru, KA}
      {Data Science Intern}{Oct 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItemNH{\textbf{Video Analyzer}: Designed and implemented a multimodal video analysis pipeline using OpenCV and MediaPipe to extract structured insights from text, audio, and visual streams.}
        \resumeItemNH{\textbf{Blog Generation Model}: Built an SEO-oriented blog generation system leveraging OpenAI and Gemini GPT APIs, integrating Wikipedia and ArXiv agents to ensure factual consistency and reliable knowledge grounding.}
        \resumeItemNH{\textbf{Image Generation Model} (Picture Book): Developed an AI-powered image generation pipeline using Stable Diffusion and PyTorch to create illustrated visual narratives for automated storytelling applications.}        
        \resumeItemNH{\textbf{Article Classifer} (Rule-Based): Engineered a rule-based NLP article classification system that accurately categorized content without supervised ML models, reducing computational overhead while maintaining high precision.}
      \resumeItemListEnd
    \resumeSubheading
      {MIT-WPU Institute of Artificial Intelligence}{Pune, MH}
      {Artificial Intelligence Research Intern}{August 2024 -- Dec 2025}
      \resumeItemListStart
        \resumeItemNH{Implemented the Snail Homing and Mating Search (SHMS) algorithm in code, translating a mentor-proposed optimization concept into a complete, working computational framework.}
        \resumeItemNH{Extended SHMS to multi-objective optimization, benchmarking performance across ZDT test suites and analyzing Pareto-front convergence and diversity.}
        \resumeItemNH{Authored peer-reviewed chapters on \textit{Normal Distribution} and \textit{Weighted Combination Models} to Springer's 'The Encyclopedia of Engineering Optimization and Heuristics'}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI-Driven Molecular Generation Pipeline (B.E. Capstone Project)}{\href{https://github.com/TejasMankeshwar/BE_Proj.git}{GitHub}}
      {Python, PyTorch, Reinforcement Learning, RDKit, SMILES}{}
      \resumeItemListStart
        \resumeItemNH{Designed and developed an end-to-end AI pipeline that ingests molecules in standardized SMILES format (CSV) and autonomously generates novel drug-like molecules with optimized properties.}
        \resumeItemNH{Architecture comprises three parallel components: a \textbf{Generator Engine} (analyzes molecular structure and generates new candidates), a \textbf{Surrogate Model} (predicts molecular properties and assigns scores), and a \textbf{Reinforcement Learning module} (evaluates generated molecules and feeds reward signals back to the generator).}
        \resumeItemNH{\textbf{My Contribution:} Orchestrated, designed, and implemented all three ML/AI models from scratch. Currently serving as \textbf{Team Lead}, overseeing end-to-end project execution, task delegation, and technical direction across the team.}
      \resumeItemListEnd

    \resumeSubheading
      {Trading Intel — AI-Powered Stock Analysis Platform}{\href{https://github.com/TejasMankeshwar/Stock_Analysis.git}{GitHub}}
      {Python, FastAPI, React, Scikit-learn, Random Forest, Pandas, yfinance, Recharts}{}
      \resumeItemListStart
        \resumeItemNH{Developed a full-stack AI platform delivering deterministic stock price projections for Nifty 50 companies across multiple time horizons (1W, 1M, 3M) using a \textbf{Random Forest Regressor} ensemble.}
        \resumeItemNH{Achieved \textbf{80\% prediction accuracy} during testing phase, validated through backtesting on 2 years of historical NSE data; engineered features include MACD, RSI, Bollinger Band Width, and EMA.}
        \resumeItemNH{Built a high-performance \textbf{FastAPI} backend with an in-memory caching mechanism for low-latency responses, and a responsive \textbf{React} dashboard visualizing actual vs.\ predicted price trends with custom confidence scoring.}
      \resumeItemListEnd

    \resumeSubheading
      {VistaDrive — Scenic Route Generator}{\href{https://github.com/TejasMankeshwar/VistaDrive.git}{GitHub}}
      {Python, OSMnx, NetworkX, Streamlit, Folium, GeoPy, GeoPandas, Google Maps API}{}
      \resumeItemListStart
        \resumeItemNH{Built a geospatial web application that generates optimized scenic driving loops of user-defined distances, prioritizing primary/secondary road networks extracted from \textbf{OpenStreetMap} via \textbf{OSMnx}.}
        \resumeItemNH{Engineered a graph-based pathfinding engine using \textbf{NetworkX} (Dijkstra's algorithm) with a geometric waypoint generation algorithm using spherical bearing-distance calculations to produce seamless 4-point loop routes.}
        \resumeItemNH{Integrated \textbf{Folium} for interactive spatial visualization; implemented a caching layer for road graph data to reduce API latency, with export support for KML files and Google Maps deep-linking.}
      \resumeItemListEnd

    \resumeSubheading
      {Chess Simulator \& AI Analysis Tool}{\href{https://github.com/TejasMankeshwar/Chess_Auto.git}{GitHub}}
      {Python, Pygame, python-chess, Stockfish (UCI Protocol)}{}
      \resumeItemListStart
        \resumeItemNH{Developed a fully functional desktop chess simulator with a responsive 2D GUI using \textbf{Pygame}, featuring intuitive drag-and-drop mechanics, board rotation, and a move-undo system.}
        \resumeItemNH{Integrated the \textbf{Stockfish UCI engine} for real-time best-move suggestions and positional evaluation; implemented a dynamic evaluation bar visualizing material/positional advantage (centipawns) with mate-threat detection.}
        \resumeItemNH{Handled asynchronous engine communication to prevent GUI lag, maintaining 60 FPS; automated asset pipeline via \textbf{urllib} to fetch and process public-domain piece assets from Wikimedia Commons.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------Publications-----------------
\section{Publications}
  \resumeSubHeadingListStartBullets

    \resumeSubItem{Tejas Mankeshwar (2025). ``Normal Distribution.''}
      {Book chapter authored for \textit{The Encyclopedia of Engineering Optimization and Heuristics}, Springer. Covers mathematical foundations, classifications, and applications in statistics and AI/ML.}

    \resumeSubItem{Tejas Mankeshwar (2025). ``Weighted-Sum Method.''}
      {Book chapter authored for \textit{The Encyclopedia of Engineering Optimization and Heuristics}, Springer. Discusses scalarization techniques for multi-objective optimization, Pareto fronts, and engineering applications.}

    \resumeSubItem{Prajakta Gunjal, Tejas Mankeshwar, Girija Chiddarwar, Bhushan Anokar (2025).}
      {\textit{High-Accuracy Classification of Pancreatic Cancer Subtypes Using Feature Selection and Optimized Machine Learning on High-Throughput Gene Expression Data}. Research paper proposing an optimized ML-based biomedical classification pipeline.}

    \resumeSubItem{Tejas Mankeshwar, Girija Chiddarwar, Anuj Dengale, Anvita Kashikar, Esha Ratnaparkhi (2025).}
      {\textit{Transforming Drug Discovery and Development: The Synergistic Role of AI, Machine Learning, Deep Learning, and Quantum Computing}. Review paper on AI/ML and quantum computing across the drug discovery pipeline.}

    \resumeSubItem{Varad Marne, Yash Khetal, Tejas Mankeshwar, Soham Miniyar (2023).}
      {\textit{Review of Dynamic Wireless Power Transfer Systems for Electric Vehicles and Its Application in India}. Review paper analyzing DWPT technologies and deployment challenges in India.}

  \resumeSubHeadingListEnd


  
% %-----------EXTRACURRICULARS-----------------
% \section{Involvement}
%   \resumeSubHeadingListStartBullets
%     \resumeSubItem{Google Developer Groups (GDG) India --- Organizing Committee Lead}
%       {Led a 48-member organizing committee, overseeing planning, timelines, and execution of technical and community initiatives. Spearheaded 4 large-scale events, including an international developer event, a national-level coding competition, and a month-long DSA teaching workshop. Fostered peer-to-peer learning and strengthened the local developer ecosystem.}

%     \resumeSubItem{Club of Developers and Engineers (CODE) --- Project Head}
%       {Led consultancy-driven development teams and served as primary point of coordination for clients. Successfully delivered 6+ industry-standard projects, managing project planning, task delegation, timelines, and quality assurance to meet client requirements.}
%   \resumeSubHeadingListEnd

  
%-----------AWARDS-----------------
\section{Achievements \& Honors}
  \resumeSubHeadingListStartBullets

    \resumeSubItem{Winner --- PES Modern College Hackathon}
      {Built an AI-enabled social NGO emergency interconnection platform using Google Earth and LLM-based services to enable real-time coordination during crises.}

    \resumeSubItem{2nd Place --- MIT-ADT University Ideathon}
      {Developed \textit{Legal-Saathi}, an AI-powered legal aid platform to help citizens understand Indian law and judiciary processes, featuring document upload and simplified legal explanations for non-technical users.}

    \resumeSubItem{3rd Place --- IMCC Hackathon}
      {Created \textit{NeXstep}, a demand forecasting and smart pricing system for retail and wholesale inventory optimization using demand probability modeling and competitor price analysis.}

    \resumeSubItem{Multiple Hackathon Winner}
      {Secured \textbf{8+ hackathon wins} across national-level competitions, recognized for innovation in AI-driven platforms, optimization, and real-world problem solving.}

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      {Python, C++, C, Java, JavaScript, R, MATLAB}

    \resumeSubItem{AI / Machine Learning}
      {Machine Learning, Deep Learning, Natural Language Processing (NLP), Large Language Models (LLMs), Reinforcement Learning, Feature Selection, Model Optimization, Statistical Modeling}

    \resumeSubItem{Frameworks \& Libraries}
      {PyTorch, Hugging Face Transformers, OpenCV, Flask, Streamlit}

    \resumeSubItem{Web \& Backend Technologies}
      {FastAPI, React, JavaScript, HTML, CSS, Bootstrap}

    \resumeSubItem{Databases \& Search}
      {MySQL, MongoDB, Elasticsearch}

    \resumeSubItem{Cloud \& DevOps}
      {AWS (EC2, Lambda), Docker, Linux, Git, Google Colab}

    \resumeSubItem{Optimization \& Algorithms}
      {Multi-Objective Optimization, Heuristic Algorithms, MOSHMS, ZDT, DTLZ Benchmarks, Pareto Optimization}

    \resumeSubItem{Tools \& Platforms}
      {GitHub, VS Code, Jupyter Notebook, LaTeX}

  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}